---
title       : Births by five-year age group of mother, major area, region and country, 1950-2100
subtitle    : Worlds Population Prospect, United Nations
author      : shahramjoon
job         : Data Scientist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz, shiny, interactive]    # {mathjax, quiz, bootstrap}        
ext_widgets :  {rCharts: ["libraries/highcharts", "libraries/polycharts",libraries/nvd3", "libraries/morris"]} 
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Abstract
> * Data is provided from United Nation, Population Divsion  <a href="http//http://esa.un.org/wpp/Excel-Data/fertility.htm">click here to go to United Nations website</a>
> * Data presents number of Birth By 5 year age group of Mother between 1950-2010
> * Mother Age is categorized to 5 boundaries:    15-19 ,  20-24,     25-29,     30-34,    35-39,    40-44,    45-49
> * Data is from 199 countries , grouped to many different geograhical areas and continents, total of 36 areas, one is WORLD Population.   
> * Data covers births between 1950-2010, in 12 groups covering 5 years per group 
> * Application is using ShinyApp development framework.link to application <a href="https://shahramjoon.shinyapps.io/MyApp">here</a>
> * It provides a user interface that viewer can choose his/her own particular country or region from Drop Down. 
> * After user makes the choice, a plot is refresh on right side, presenting data related to user's chosen country or region. Plot is located on tab labeled "country/region" 
> * Supporting Data of Plot related to user's chosen country or region is refreshed on a tab lableled Table

--- 

##  Top Ten Most Powerful Countries in the World

Graph is showing number of Births based on Mother Age 

```{r  nvd3plot22, results = 'asis', comment = NA, message = F, echo = F }
library(reshape2)
library(plyr)
library(rCharts)
library(knitr)

fertility <- read.table("fertility.csv", 
                        sep=",", 
                        header=TRUE, 
                        na.strings=c("NA","#DIV/0!", ""), 
                        stringsAsFactors=FALSE,
                        fileEncoding="latin1")




country <- unique(fertility[fertility$Notes=="c", c("Area")])
region <- unique(fertility[is.na(fertility$Notes), c("Area")])

fertility$Notes <- factor(fertility$Notes)
fertility$Period <- factor(fertility$Period)
fertility$Variant <- NULL
fertility <- fertility [1:2814,]
country <- sort(country)
region <- sort(region)

data <- melt (fertility, id.vars=c("Area","Period") ,
              measure.vars=c("g15_19","g20_24", "g25_29", "g30_34", "g35_39", "g40_44", "g45_49"), 
              variable.name="agegroup", value.name="cnt")


summarydata <- ddply ( data, c("Area", "Period"), summarise, total=sum(cnt))

top10 <- c ("United States of America" , "China" , "India", "Germany", "United Kingdom"  , "France" , "Japan" , "Russian Federation" , "Brazil" , "Italy" )

top10data <- ddply ( subset(data, Area %in% top10), c("Area", "Period"), summarise, total=sum(cnt))

n1 <- nPlot(total~Period, group="Area", data=top10data, type = "multiBarChart")
  

top10dataAgeGroup <- ddply ( subset(data, Area %in% top10), c("Area", "agegroup"), summarise, total=sum(cnt))



n2 <- nPlot(total~agegroup, group="Area", data=top10dataAgeGroup, type = "multiBarChart")
n2$xAxis(axisLabel = 'Mother Age Group')
n2$yAxis(axisLabel = 'Birth(Thousands)')
n2$chart(reduceXTicks = FALSE)
n2$xAxis(staggerLabels = TRUE)

  
n2$show('inline')


```

---

##  Top Ten Most Powerful Countries in the World

Graph is showing number of Births based on Mother Age 


```{r  nvd3plot23, results = 'asis', comment = NA, message = F, echo = F }

n3 <- nPlot(total~Area, group="agegroup", data=top10dataAgeGroup, type = "multiBarChart")
n3$xAxis(axisLabel = 'Country')
n3$yAxis(axisLabel = 'Birth(Thousands)')

n3$chart(reduceXTicks = FALSE)
n3$xAxis(staggerLabels = TRUE)


n3$show('inline')


```

---

##  Seven continents and WORLD

Graph is showing Total Number of Births between 1950-2010 

```{r  nvd3plot, results = 'asis', comment = NA, message = F, echo = F }

r <- c ( "AFRICA", "EUROPE", "ASIA", "LATIN AMERICA AND THE CARIBBEAN" , "Australia/New Zealand", "WORLD", "NORTHERN AMERICA", "Central America")

continentaldata <- ddply ( subset(data, Area %in% r), c("Area", "Period"), summarise, total=sum(cnt) )

n6 <- nPlot(total~Period, group="Area", data=continentaldata, type = "multiBarChart")
n6$xAxis(axisLabel = 'Year Group')
n6$yAxis(axisLabel = 'Birth(Thousands)')
n6$chart(reduceXTicks = FALSE)
n6$xAxis(staggerLabels = TRUE)
n6$show('inline')


```
 
